{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or, How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-08-01 thesis/landslide.tex
and to prune
KEEP_RUNNING_DPORS_CHOSEN_TID

		and prune the second interleaving

@@

Landslide implements this check in {\tt equiv\_already\_explored()}.
This corresponds to the {\em sleep sets} optimization described by prior work \cite{partial-order-methods,dpor,optimal-dpor},
so named because it effectively puts $T_1$ ``to sleep'' until after the true conflicting access in $t_c$.
Landslide's implementation differs from prior work by not explicitly tracking
sets of reordered threads and memory accesses they should expect to conflict with,
and instead identifies where the reduction should take place in subsequent iterations of DPOR.
Further optimizations such as {\em source sets} and {\em wakeup trees},
which achieve optimality (i.e., executing exactly one interleaving per equivalence class) \cite{optimal-dpor}
are not yet implemented,
although to the best of my knowledge,
they provide further reduction only in cases of 3 or more threads;
I suspect (without proof) that sleep-set DPOR is optimal for 2 threads.

>>>>

		and to prune the second interleaving

@@

Landslide implements this check in {\tt equiv\_already\_explored()}.
This corresponds to the {\em sleep sets} optimization described by prior work \cite{partial-order-methods,dpor,optimal-dpor},
so named because it effectively puts $T_1$ ``to sleep'' until after the true conflicting access in $t_c$.
Landslide's implementation differs from prior work by not explicitly tracking
sets of reordered threads and memory accesses they should expect to conflict with,
and instead identifies where the reduction should take place in subsequent iterations of DPOR.
% KEEP_RUNNING_DPORS_CHOSEN_TID
This approach also relies on the search ordering strategy ({\tt arbiter\_choose()})
to prefer scheduling the thread previously chosen for reordering by DPOR,
to force whatever its conflicting memory access was to happen before the other, preempted thread gets a chance to run.
Further optimizations such as {\em source sets} and {\em wakeup trees},
which achieve optimality (i.e., executing exactly one interleaving per equivalence class) \cite{optimal-dpor}
are not yet implemented,
although to the best of my knowledge,
they provide further reduction only in cases of 3 or more threads;
I suspect (without proof) that sleep-set DPOR is optimal for 2 threads.
